---
title: "Vacine Outbreaks"
author: "carlos Tonhatti"
date: "August 9, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Historic of anti-vax
- In 1998, Andrew Wakefield  colleagues in Lancet "Vacine causes autism"
- Immediately after a series of papers using epidemilogical data refuse this suggestion.
- In 2010 Lancet retracted the paper due anti- ethical methods.

I will show the impact of this in increase of cases. 

```{r}
library(stringr)
library(reshape2)
library(ggplot2)
library(dplyr)
library(nominatim)
vacine<-read.csv("vacine.csv")

vacineClear<-vacine[,c(1:13)]

vacineClear$Outbreak<- gsub(".*[Ff]lu*","flu",vacineClear$Outbreak) 
vacineClear$Outbreak<-as.factor(vacineClear$Outbreak)
vacineClear$Long<-as.numeric(as.vector(vacineClear$Long))



tmp_date<-str_split(vacineClear$Date,"-")

vacineClear$Country<-str_trim(vacineClear$Location.1.1)
extractDate<-function(x){
     return(x[1])
}

tmp_date2<-sapply(tmp_date,extractDate)

tmp_date2[grep("\\.",tmp_date2)]<-as.numeric(tmp_date2[grep("\\.",tmp_date2)])

# imputacao de data
tmp_date2[grep("/",tmp_date2,invert=TRUE)]<-paste0("1/",tmp_date2[grep("/",tmp_date2,invert=TRUE)])

vacineClear$Date<-as.Date(paste0("1/",tmp_date2), format="%d/%m/%Y")

vacineClear$Year<-as.numeric(format(vacineClear$Date,"%Y"))


vacine_tbl<-tbl_df(vacineClear) 

# tabela cases
resu<-vacine_tbl %>%
  group_by(Year,Category) %>%
  summarise(Cases=sum(Cases))
 library(plotly)














```
## Overtime
```{r}
ggplotly(ggplot(resu,aes(x=Year,y=Cases,color=Category)) + geom_line())
```



## References 

- Wakefield AJ, Murch SH, Anthony A, Linnell J, Casson DM, Malik M, et al. Ileal-lymphoid-nodular hyperplasia, non-specific colitis, and pervasive developmental disorder in children. Lancet. 1998;351:637–41.

Data from : https://www.cfr.org/interactives/GH_Vaccine_Map/ 